### 2012-11-12 paper.tex
half of mantri done

\documentclass[]{article}
\renewcommand{\rmdefault}{ptm}
%\usepackage[hmargin=30mm]{geometry}
\usepackage{tabularx}

@@

\begin{table}[here]
\centering
\begin{tabularx}{\textwidth}{| X | X | }
\hline
Topic of Survey								& 	Cloud Computing\\
\hline
Length of Survey							& 	15 pages\\
\hline
First team member's matriculation number	&	U096833E\\
\hline
First team member's name					&	LAURENCE PUTRA FRANSLAY\\
\hline
Sections done by first member				& 	1.1.x\\
\hline
Second team member's matriculation number	&	\\
\hline
Second team member's name					&	\\
\hline
Sections done by second member				& 	\\
\hline

@@

\subsubsection{Implementation}
There are various ways to implement MapReduce, and it generally depends on the hardware available, and the following describes the implementation that is done at Google.\\

The data is first split into chunks of 16MB to 64MB, dependent on user input, and the program is started up multiple times on the cluster that is assigned for that task. Of all the copies of the program that is started up, one of it would be assigned the master role, and has the job of assigning idle workers to a task. When an idle worker is assigned a \emph{map} task, it will then process the corresponding chunk of data, and pass each key-value pair to the \emph{map} function. The intermediate key-value pairs produced by the \emph{map} function is then temporarily stored in memory. The intermediate key-value pairs stored in memory are then regularly pushed onto local storage, and their stored locations are then passed to the master program to keep track of. The master program will then assign \emph{reduce} tasks to the worker programs, who will sort the intermediate data based on their key's before performing the actual processing. If the amount of data is too large, it will sometimes be done externally by another program. After this processing is completed, the reduce function will process the sorted intermediate data, and return the output and write it to a global storage. Once all the map tasks and reduce tasks are finally completed, the master program will wake up the user program and continue processing in the user program. The result of the MapReduce call will be be available in the \emph{n} output files generated by the \emph{n} reduce tasks, and would generally be fed as input to another MapReduce function call.\\

@@

\subsubsection{Fault tolerance}
The MapReduce library is intended to process a massive amount of data using massive computational resources. Hence, there is a requirement to make this system able to recover from faults too. \\

@@

Another addon which may come in useful to most users is that the partition files are sorted in ascending order. This would allow future users of the file to easily look for the data they require within the file.

A useful addon to reduce network I/O would be the combiner. In essence the combiner just runs the \emph{reduce} function right after \emph{map}, and write it to the intermediate output file. For example, in a program that counts the total number of words there are might have plenty of duplicate words due to the map function. What the combiner  would do is to merge this data together first so that instead of sending thousands of records over, it can be sent as a few records.

\subsection{Addition enhancement to MapReduce}
%each of these sections should take around 1.5 to 2 pages.
\subsubsection{Camdoop}
%Preprocessing instead of post processing

\subsubsection{Mantri}
% Load balancing tasks and reduce the effects caused by outliers

>>>>

\documentclass[]{article}
\renewcommand{\rmdefault}{ptm}
%\usepackage[hmargin=30mm]{geometry}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{wrapfig}

@@

\begin{table}[here]
\centering
\begin{tabularx}{\textwidth}{| X | X | }
\hline
Topic of Survey								& 	Cloud Computing\\
\hline
Length of Survey							& 	15 pages\\
\hline
First team member's matriculation number	&	U096833E\\
\hline
First team member's name					&	LAURENCE PUTRA FRANSLAY\\
\hline
Sections done by first member				& 	1.1.x, 1.2.2\\
\hline
Second team member's matriculation number	&	\\
\hline
Second team member's name					&	\\
\hline
Sections done by second member				& 	\\
\hline

@@

\subsubsection{Implementation}
There are various ways to implement MapReduce, and it generally depends on the hardware available, and the following describes the implementation that is done at Google. However, in general, MapReduce is run on distributed systems, and generally on warehouse scale machines.\\

The data is first split into chunks of 16MB to 64MB, dependent on user input, due to the fact that the filesystem is stored in 64MB chunks, and the program is started up multiple times on the cluster that is assigned for that task. Of all the copies of the program that is started up, one of it would be assigned the master role, and has the job of assigning idle workers to a task. When an idle worker is assigned a \emph{map} task, it will then process the corresponding chunk of data, and pass each key-value pair to the \emph{map} function. The intermediate key-value pairs produced by the \emph{map} function is then temporarily stored in memory. The intermediate key-value pairs stored in memory are then regularly pushed onto local storage, and their stored locations are then passed to the master program to keep track of. The master program will then assign \emph{reduce} tasks to the worker programs, who will sort the intermediate data based on their key's before performing the actual processing. If the amount of data is too large, it will sometimes be done externally by another program. After this processing is completed, the reduce function will process the sorted intermediate data, and return the output and write it to a global storage. Once all the map tasks and reduce tasks are finally completed, the master program will wake up the user program and continue processing in the user program. The result of the MapReduce call will be be available in the \emph{n} output files generated by the \emph{n} reduce tasks, and would generally be fed as input to another MapReduce function call.\\

@@

\subsubsection{Fault tolerance}
The MapReduce library is intended to process a massive amount of data using massive computational resources. Hence, there is a requirement to make this system able to recover from faults too. However, it is worth noting in this case that Google is actually using a custom filesystem, that has the ability to recover from hardware failure due to it's usage of redundancy.\\

@@

Another addon which may come in useful to most users is that the partition files are sorted in ascending order. This would allow future users of the file to easily look for the data they require within the file. \\

A useful addon to reduce network I/O would be the combiner. In essence the combiner just runs the \emph{reduce} function right after \emph{map}, and write it to the intermediate output file. For example, in a program that counts the total number of words there are might have plenty of duplicate words due to the map function. What the combiner  would do is to merge this data together first so that instead of sending thousands of records over, it can be sent as a few records.\\

\subsection{Additional enhancement to MapReduce}
%each of these sections should take around 1.5 to 2 pages.
\subsubsection{Camdoop}
%Preprocessing instead of post processing

\subsubsection{Mantri}
% Load balancing tasks and reduce the effects caused by outliers
Mantri is a method that use used to reduce the impact that outliers have on the entire MapReduce operation. As detailed earlier, MapReduce internally handles outliers by assigning an identical task to another worker machine, in the hopes that it can complete the task earlier. These outliers may happen due to many reasons, including but not limited to heavy workload for that machine, or large quantities of hard disk I/O during that period of time. \\

Mantri works on reducing the amount of impact outliers have on the system by identifying the main causes for such outliers, which is mainly high hard disk I/O, congested network pipes, as well as a skewed assignment of task as a result of the data partitioning which is often done over a set of data that is not exactly random. Mantri has been tested on all of Bing's production cluster and has shown to have large performance benefits, speeding up more than half the jobs by 50\%. \\

Mantri basically identifies certain checkpoints that the tasks are not able to perform at the expect rate, and solves these issues by trying to solve the underlying issue causing the slowdown in performance. The figure below shows the actions taken by Mantri for each type of problem. \\
\begin{figure}[here]
	\begin{center}
		\includegraphics[width=0.9\textwidth]{mantri11.png}
		\caption{Actions taken by Mantri}
	\end{center}
\end{figure}
